---
title: "Quarto for Academics"
format: 
  revealjs:
    chalkboard: true
    multiplex: true
  html:
    code-link: true # links your funtions 
editor: visual
execute: 
  echo: true

---

## Introduction
Mine's YouTube:  https://www.youtube.com/watch?v=EbAAmrB0luA&t=372s

* chalkboard allows you to annotate your slides.
* *multiplex* Advance slides 
* by default, revealjs hides your code
* to see code, turn on echo: true 
* Highlight code: 
  - code-line-numbers
  

## Data  
* Penguin dataset 
```{r}
#| label: load-packages
#| message: false
#| include: false # do not include this code chunk  

library(tidyverse)

# https://github.com/jrnold/ggthemes
# library(remotes)
# install_github("cran/ggthemes")
# library("devtools")
# install_github(c("hadley/ggplot2", "jrnold/ggthemes"))
# library("devtools")
# install_github(c("hadley/ggplot2", "jrnold/ggthemes"))
library(ggthemes)

# install.packages("highcharter")

library(palmerpenguins)
library(gt)
```


```{r}
glimpse(penguins)
```

## Species 



```{r}

# #| label: fig-bill-dims-species
#| label: fig-bill-dims-species
#| fig-width: 5
#| fig-asp: 0.618
#| fig-alt:
#|  A scatterplot of penguins' bill depth and length, colored by
#|  species of penguins.  There is a relatively strong, linear
#|  association.
#|  fig-cap:
#|  A scatterplot of penguins' bill depth and length, colored by 
#|  species of penguins.
#|  output-location: slide 

### NOTE - Use a colon for the cross-ref:  @fig-bill-dims-species: is a scatter plot of species of penguins.

ggplot(
  penguins,
  aes(
    x = bill_length_mm, y = bill_depth_mm,
    color = species, shape = species
  )
) +
  geom_point() +
  scale_color_colorblind() +
  theme_minimal() +
  theme(legend.position = "top") +
  labs(x= "Bill length (mm)", y = "Bill depth (mm)")

```

@fig-bill-dims-species is a scatter plot of species of penguins

@fig-bill-dims-species: is a scatter plot of species of penguins.

\@ref(fig:fig-bill-dims-species) is a scatter plot of species of penguins.


## Penguins

@tbl-penguins-top10: shows the first 10 penguins from the dataset.

```{r}

# #| label: tbl-penguins-top10
#| label: tbl-penguins-top10
#| tbl-cap: First 10 penguins.

penguins |>
  slice_head(n = 10) |>
  select(species, island, bill_length_mm, bill_depth_mm) |>
  gt()  

```


## Analysis  

### Modeling results  

Some modeling results go here...  